%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

 \cventry
 {Senior Machine Learning Engineer}
 {Gamania Digital Entertainment}
 {Taipei, Taiwan}
 {Jul. 2025 - Present}
 {
     \begin{cvitems}
         \item {Built an AI agent-driven platform enabling users to autonomously plan and generate manga content.}
         \item {Developed immersive vertical-scroll webtoon reading features including AI-generated background music and sound effects.}
         \item {Implemented AI virtual character \textbf{Voice Conversion} systems for interactive content.}
     \end{cvitems}
 }

%---------------------------------------------------------
 \cventry
 {Visiting Researcher}
 {Sony Computer Science Laboratories (Sony CSL)}
 {Tokyo, Japan (Hybrid)}
 {Jun. 2025 - Oct. 2025}
 {
     \begin{cvitems}
         \item[] \footnotesize\textbf{\textcolor{teal}{Research Topics:}} \textit{\textcolor{teal}{\textbf{Music Information Retrieval, Automatic Music Transcription}}}
         \item {Proposed \textbf{VioPTT}, a lightweight cascade model for violin technique-aware transcription with a novel synthetic dataset (\textbf{MOSA-VPT}). Published at \textbf{ICASSP 2026}.}
         \item {Investigated \textbf{transfer learning} for violin AMT, showing training from scratch on instrument-specific data can match fine-tuned piano-pretrained models. Published at \textbf{ISMIR 2025}.}
     \end{cvitems}
 }

%---------------------------------------------------------
 \cventry
 {AI Engineer}
 {Gate.io}
 {Taipei, Taiwan (Remote)}
 {Oct. 2024 - May 2025}
 {}

%---------------------------------------------------------
  \cventry
    {Research Assistant \newline~\textbf{Supervisor: Dr. Li Su}} % Job title
    {Institute of Information Science, Academia Sinica} % Organization
    {Taipei, Taiwan} % Location
    {Jul. 2024 - Oct. 2024\newline~Mar. 2022 - Jun. 2023} % Date(s)
    % {Mar. 2022 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item[] \footnotesize\textbf{\textcolor{teal}{Research Topics:}} \textit{\textcolor{teal}{\textbf{Self-Supervised Learning, Medical Imaging}}}
            \item {Surveyed end-to-end \textbf{self-supervised learning} methods for decoding mental states from brain activity (fMRI).}
            \item {Conducted \textbf{distributed training} experiments on large-scale, \textbf{high-resolution 4D medical image (fMRI)} using \href{https://www.twcc.ai/intro/HPC}{\color{cyan}{\textbf{TWCC HPC}}}.}
            \item {Proposed a whole-brain feature selection method for decoding musical pitch from brain activity (fMRI) \cite{ICASSP2023}.}
        \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    % {Research \& Development - AI Engineer Intern} % Job title
    {AI Engineer Intern} % Job title
    {Tomofun} % Organization
    {Taipei, Taiwan} % Location
    {Mar. 2023 - Jul. 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item[] \footnotesize\textbf{\textcolor{teal}{Research Topics:}} \textit{\textcolor{teal}{\textbf{Computer Vision, Large Language Models, Multimodal Learning}}}
            \item {Developed an automatic \textbf{short music video generation system} for daily pet clips.}
            \item Developed a pipeline for \textbf{fine-tuning} visual language model (e.g., BLIP) and improved \textbf{visual question answering performance by 20.6\%}.
            \item {Developed APIs for \textbf{visual large language models (e.g., LLaVA)} with \href{https://github.com/ggerganov/llama.cpp}{\color{orange}\textbf{llama.cpp}}/\href{https://ollama.com/library/llava}{\color{orange}\textbf{ollama}} to generate image-caption pair datasets.}
            \item {Enhanced LLaVA image \textbf{inference speed by 250\%} with only a 3\% reduction in accuracy.}
        \end{cvitems}
    }
%---------------------------------------------------------
    
%---------------------------------------------------------
  % \cventry
  %   {Research Assistant} % Job title
  %   {Institute of Information Science, Academia Sinica} % Organization
  %   {Taipei, Taiwan} % Location
  %   {Mar. 2022 - Feb. 2023 } % Date(s)
  %   {
  %       \begin{cvitems} % Description(s) of tasks/responsibilities
  %           \item {Proposed a whole-brain feature selection method for decoding musical pitch from brain activity (fMRI) \cite{ICASSP2023}.}
  %       \end{cvitems}
  %   }
%---------------------------------------------------------

%   \cventry
%     {Freelance Penetration Tester} % Job title
%     {SAMSUNG Electronics} % Organization
%     {S.Korea} % Location
%     {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
%         \item {Conducted penetration testing on SAMSUNG Smart TV.}
%       \end{cvitems}
%       %\begin{cvsubentries}
%       %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
%       %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%       %\end{cvsubentries}
%     }

% %---------------------------------------------------------
\end{cventries}
