%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
% \cvsubsection{International}



%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\renewcommand{\section}[2]{} %add this line to remove 'reference' title

\begin{thebibliography}{9}

\bibitem{ICASSP2026}
Wang, T. K., \textbf{Peng, Y. P.}, Su, L., \& Cheung, V. K. M., 
"VioPTT: Violin Technique-Aware Transcription from Synthetic Data Augmentation," 
in Proc. IEEE International Conference on Acoustics, Speech and Signal Processing 2026 (ICASSP'26).

\bibitem{ISMIR2025}
\textbf{Peng, Y. P.}, Wang, T. K., Su, L., \& Cheung, V. K. M., 
"Is Transfer Learning Necessary for Violin Transcription?," 
in Int. Society for Music Information Retrieval Conf. 2025 (ISMIR'25) - Late Breaking/Demo.

\bibitem{ARXIV2025}
\textbf{Peng, Y. P.}, Cheung, V. K. M., \& Su, L., 
"Whole-Brain Transferable Representations from Large-Scale fMRI Data Improve Task-Evoked Brain Activity Decoding," 
arXiv preprint arXiv:2507.22378, 2025.

\bibitem{DAFX2024}
Lee, Y. S.*, \textbf{Peng, Y. P.*}, Wu, J. T., Cheng, M., Su, L., \& Yang, Y. H., 
"Distortion recovery: A two-stage method for guitar effect removal," 
in Proc. Int. Conf. Digital Audio Effects 2024 (DAFx'24). (* equally contributed)

\bibitem{ICASSP2023}
Cheung, V. K.*, \textbf{Peng, Y. P.*}, Lin, J. H., \& Su, L., 
"Decoding Musical Pitch from Human Brain Activity with Automatic Voxel-Wise Whole-Brain FMRI Feature Selection," 
in Proc. IEEE International Conference on Acoustics, Speech and Signal Processing 2023 (ICASSP'23). (* equally contributed) 


% \bibitem{texbook}
% Donald E. Knuth (1986) \emph{The \TeX{} Book}, Addison-Wesley Professional.

\end{thebibliography}
